Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-02-09 text/paper/revision_01/paper.tex
K2 cover letter; sigh...

\paragraph{Pictorial Effects.} It is often possible to present
different numbers of links between icons in pictures like in
Figures~\ref{fig:AS-distinguishing-pics}
and~\ref{fig:ES-distinguishing-pics}, without changing the
truth-values of relevant readings. Indeed, the pictorial material used
in previous studies differed in this respect, and that might explain
some of the differences in results. If that is so, then we cannot
ascribe the effects reported by
\citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev} to the availability of local
readings with certainty. \citet{ChemlaSpector2010:Experimental-Ev}
also acknowledge the possibility that the \emph{typicality} of a
picture with respect to some meaning may affect graded truth-value
judgments: a sentence like \emph{Some of the 10 marbles are white} is
more typical, intuitively speaking, in a situation with 4 white
marbles than in a situation with 8 or 9 white marbles \citep[for more
on the controversial interpretation of ``typicality'' in this context
see][]{Tielvan-Tiel2014:Quantity-Matter,Cummins2014:Typicality-made,
  ,Franke2014:Typical-use-of-}. \citeauthor{ChemlaSpector2010:Experimental-Ev}
show that graded judgments of \as-sentences differ significantly for
different pictures that agree on the truth value of relevant readings
but differ with respect to the amount of connections between
icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
typicality of the pictorial material can account for these
differences, but submit that this does not explain away the high
acceptance of pictures like Figure \ref{fig:weak}.

>>>>

\paragraph{Pictorial Effects.} It is often possible to present
different numbers of links between icons in pictures like in
Figures~\ref{fig:AS-distinguishing-pics}
and~\ref{fig:ES-distinguishing-pics}, without changing the
truth-values of relevant readings. Indeed, the pictorial material used
in previous studies differed in this respect, and that might explain
some of the differences in results. If that is so, then we cannot
ascribe the effects reported by
\citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev} to the availability of local
readings with certainty. \citet{ChemlaSpector2010:Experimental-Ev}
also acknowledge the possibility that the \emph{typicality} of a
picture with respect to some meaning may affect graded truth-value
judgments. \citeauthor{ChemlaSpector2010:Experimental-Ev} show that
graded judgments of \as-sentences differ significantly for different
pictures that agree on the truth value of relevant readings but differ
with respect to the amount of connections between
icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
typicality of the pictorial material can account for these
differences, but submit that this does not explain away the high
acceptance of pictures like Figure \ref{fig:weak}.\footnote{It is a
  matter of controversy what ``typicality'' actually is. Intuitively,
  a sentence like \emph{Some of the 10 marbles are white} is more
  ``typical'' or ``natural'' in a situation with 4 white marbles than
  in a situation with 8 or 9 white marbles. These intuitions have been
  tested and reported as ``typicality'' or ``naturalness'' data for a
  number of quantifiers
  \citep{DegenTanenhaus2011:Making-Inferenc,Tielvan-Tiel2012:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter,DegenTanenhaus2012:Processing-Scal}. It
  remains controversial, however, what exactly it is that is measured
  and labelled ``typicality'' in these tasks
  \citep[c.f.][]{Cummins2014:Typicality-made,Franke2014:Typical-use-of-}.}
